### 2020-02-20 docs/papers/osr/body.tex
more text

\newcommand{ironstar}{Iron{\star}}
\newcommand{bepsilon}{B^{\epsilon}}

@@

\comment{Discuss the tree hierarchy in veribetrfs}
Figure~{diagram} shows the richest refinement hierarchy in the
{\veribetrfs} system.
The top refinement explains how queries searching a {\bepsilon}tree
structure give it behavior equivalent to a map,
while abstracting the internal structure of tree nodes as infinite
maps.
The next layer explains how nodes can be implemented in finite space
with pivots; note that this layer disregards the {\bepsilon}tree structure,
since those correctness arguments are already dispatched in the
layer above.
The pivot layer assumes that nodes are abstract datatypes that can
be passed through disk storage, which of course is an abstraction of
the real disk. The next layer shows how marshalling can provide the
same abstract data types while passing byte strings through disk storage.

@@

The developer uses

@@

>>>>

\newcommand{ironstar}{Iron{\star}}
\newcommand{bepsilon}{B^{\epsilon}}
\newcommand{veribetrfs}{\texttt{\textit{veri}betrfs}}

@@

\comment{Discuss the tree hierarchy in veribetrfs}
Figure~\ref{betreerefinement} shows the richest refinement hierarchy in the
{\veribetrfs} system.
The top refinement explains how queries searching a {\bepsilon}tree
structure give it behavior equivalent to a map,
while abstracting the internal structure of tree nodes as infinite
maps.
The next layer explains how nodes can be implemented in finite space
with pivots; note that this layer disregards the {\bepsilon}tree structure,
since those correctness arguments are already dispatched in the
layer above.
The pivot layer assumes that nodes are abstract datatypes that can
be passed through disk storage, which of course is an abstraction of
the real disk. The next layer shows how marshalling can provide the
same abstract data types while passing byte strings through disk storage.

@@

The developer creates the intermediate state machines as
``interface boundaries'' that separate concerns.
She organizes the bulk of the proof artifact
by slicing it across the axis of abstraction.

Of course, the proof artifact can also be orthogonally organized
by module.
In {\veribetrfs},
the {\bepsilon}tree refinement stack of Figure~\ref{betreerefinement}
has a (simpler) sibling that reasons about a disk block caching module.

@@

\subsubsection{A day in the life of a verification engineer.}
What is it like to develop software in this style?

Define a state machine.
- it's immutable datatypes; get comfortable with abstraction.
State a refinement.
- it's a boilerplate induction pattern.
Assert its proof.
- Start with {} -- see how far automation takes you.
- Probably a simple case breakdown. Write an if or case statement!
Diagnose
- bisection debugging! This is an exciting part of the story;
  forward-reference it. Contrast it with proof-goal manipulation
  (Coq/Isabelle/TLAPS) or counterexample deconstruction.
Develop an invariant
- I bet you're missing an invariant
Patch up a proof
- bugs in definitions (off by one errors)
- witnesses
- automation syntactic triggering

recursion vs. quantification story
